\renewcommand{\bibname}{References}
\begin{thebibliography}{99}

\raggedright

\bibitem{bpmn}
\textit{Business Process Model and Notation
(BPMN)}, OMG Document Number: formal/2011-01-03, January 2011. [Online] Available: http://www.omg.org/spec/BPMN/2.0/PDF

\bibitem{activiti}
\textit{Activiti} [Online]. Available: http://activiti.org/

\bibitem{rails}
\textit{Ruby on Rails} [Online]. Available: http://rubyonrails.org/

\bibitem{git}
\textit{Git}. [Online] Available: http://www.git-scm.com

\bibitem{github}
\textit{GitHub}. [Online] Available: http://www.github.com

\bibitem{rails-article}
D. Geer, ``Will Software Developers Ride Ruby on Rails to Success?'', \textit{IEEE Computer}, vol. 39, no. 2, pp. 18 -- 20, Feb. 2006.

\bibitem{erb}
S. Ellis, ``An Introduction to ERB Templating``. [Online] Available: http://www.stuartellis.eu/articles/erb/

\bibitem{haml}
(2013). \textit{Haml}. [Online] Available: http://haml.info/

\bibitem{rbpm}
\textit{rbpm | RubyGems.org} [Online]. Available: https://rubygems.org/gems/rbpm

\bibitem{stonepath}
\textit{Introduction to the Stonepath Workflow Modeling Methodology},
CodeSherpas Inc., Leesberg, VA, 2009. [Online] Available: https://github.com/bokmann/stonepath/raw/master/stonepath.pdf

\bibitem{ruote}
(2013). \textit{Ruote}. [Online] Available: http://ruote.rubyforge.org/

\bibitem{ruote-kit}
K. Kalmer. (2013). \textit{RuoteKit}. [Online] Available: https://github.com/kennethkalmer/ruote-kit

\bibitem{ruote-synchronize}
A. Kohlbecker. (2013). \textit{ruote-synchronize}. [Online] Available: https://github.com/adrienkohlbecker/ruote-synchronize

\bibitem{jbpm}
\textit{jBPM jPDL User Guide} [Online]. Available: http://docs.jboss.com/jbpm/v3/userguide/

\bibitem{devise}
(2014). \textit{devise} [Online]. Available: http://devise.plataformatec.com.br/

\bibitem{omniauth}
INTRIDEA Inc. (2014). \textit{OmniAuth: Standardized Multi-Provider Authentication} [Online]. Available: https://github.com/intridea/omniauth

\bibitem{devise-openid}
N. Budin. (2014). \textit{devise\_openid\_authenticatable} [Online]. Available: https://github.com/nbudin/devise\_openid\_authenticatable

\bibitem{omniauth-ldap}
P. Yu. (2012). \textit{omniauth-ldap} [Online]. Available: https://github.com/intridea/omniauth-ldap

\bibitem{stonewall}
D. Bock. (2010). \textit{Stonewall}. [Online] Available: https://github.com/bokmann/stonewall

\bibitem{cancan}
R. Bates. (2013). \textit{CanCan}. [Online] Available: https://github.com/ryanb/cancan

\bibitem{authority}
N. Long. (2014). \textit{Authority}. [Online] Available: https://github.com/nathanl/authority

\bibitem{pundit}
(2014). \textit{Pundit}. [Online] Available: https://github.com/elabs/pundit

\bibitem{acts_as_relation}
H. Zamani. (2013). \textit{Acts as relation} [Online]. Available: http://hzamani.github.io/acts\_as\_relation/

\bibitem{heritage}
T. Dippel. (2013). \textit{Heritage} [Online]. Available: https://github.com/dipth/Heritage

\bibitem{capybara}
\textit{Test your app with Capybara} [Online]. Available: http://jnicklas.github.io/capybara/

\bibitem{watir}
\textit{Watir.com, Web Application Testing in Ruby} [Online]. Available: http://watir.com/

\bibitem{timecop}
T. Jeffery. (2014). \textit{timecop} [Online]. Available: https://github.com/travisjeffery/timecop

\bibitem{resque}
(2014). \textit{Resque} [Online]. Available: https://github.com/resque/resque

\bibitem{delayed_job}
(2014). \textit{Delayed::Job} [Online]. Available: https://github.com/collectiveidea/delayed\_job

\bibitem{queue_classic}
R. Smith. (2014). \textit{queue\_classic} [Online]. Available: https://github.com/ryandotsmith/queue\_classic

\bibitem{clockwork}
(2014). \textit{Clockwork - a clock process to replace cron} [Online]. Available: https://github.com/tomykaira/clockwork

\bibitem{railroad}
J. Smaldone. (2007). \textit{RailRoad}. [Online] Available: http://railroad.rubyforge.org/

\bibitem{graphviz}
\textit{GraphViz}. [Online] Available: http://www.graphviz.org/

\bibitem{ruby-graphviz}
V. Hokstad. (2013). \textit{Ruby-Graphviz}. [Online] Available: https://github.com/glejeune/Ruby-Graphviz/

\bibitem{expirable}
B. MacDonell. (2014). \textit{expirable} [Online]. Available: https://github.com/WorkflowsOnRails/expirable

\bibitem{aasm_statecharts}
B. MacDonell. (2014). \textit{aasm\_startcharts} [Online]. Available: https://github.com/WorkflowsOnRails/aasm\_statecharts

\bibitem{aasm_progressable}
B. MacDonell. (2014). \textit{aasm\_progressable} [Online]. Available: https://github.com/WorkflowsOnRails/aasm\_progressable

\bibitem{aasm_actionable}
B. MacDonell. (2014). \textit{aasm\_startcharts} [Online]. Available: https://github.com/WorkflowsOnRails/aasm\_statecharts

\bibitem{taverna-website}
(2009). \textit{Taverna}. [Online] Available: http://www.taverna.org.uk/

\bibitem{offut}
P. Ammann and J. Offutt. ``Input Space Partitioning,'' in \textit{Introduction to Software Testing}, $1^{st}$ ed. Cambridge: Cambridge University Press, 2008, ch. 4, pp. 150 -- 169.

\bibitem{rspec}
(2014). \textit{RSpec}. [Online] Available: https://github.com/rspec/rspec


\end{thebibliography}

% If you have your general bibliography in a separate file mybib
% and you wish to use the plain style (see BIBTeX)
%    \bibliographystyle{cacm}
%    \bibliography{mybib}
%    \addcontentsline{toc}{chapter}{\bibname}

%%  LocalWords:  Taverna uk
