\documentclass[document.tex]{subfiles}
\begin{document}

\title{Stateful Workflow-based\\Application Development}
\author{
  Alexander Clelland (100764969), \\
  Brendan MacDonell (100777952)
}
\copyrightfalse % do not produce a separate copyright page

% Here you insert the stuff that comes before the preface
% Each preface section is contained in a \prefacesection and starts on a
% new page.  These are numbered using Roman numerals.
% If there are no such pages, do not remove the \beforepreface command
% since it creates the title page.
\beforepreface

\chapter*{Abstract}
Most companies and organizations have business processes that are carried out as a series of steps, often by people in specific roles. Such processes are known as workflows. As information technology has become a part of modern business, these processes have come to be managed by software applications. Although some software platforms provide developers with tools to quickly implement maintainable workflow-based software, the Ruby on Rails web application framework has little such tooling. Systems involving business processes thus tend to be implemented on Rails in an ad hoc manner, decreasing development speed and maintainability. An appropriate workflow platform is needed for Rails.

To create a platform, a pair of prototypes and a case study application were first created to evaluate the tooling available for Rails. Several opportunities for improvement were identified, and reusable components were extracted from the case study to meet these needs. These components were combined with existing third-party components to define a new platform. Finally, the platform was validated by using it to construct a proof-of-concept workflow-based application. The new platform provides capabilities that were previously unavailable for Rails developers, such as the ability to visualize the workflows driving an application as statecharts.


\chapter*{Acknowledgements}

\todo {Finish this}

We would like to extend our thanks to our supervisor, Professor Esfandiari.
His suggestions and feedback never failed to steer us to fruitful avenues of inquiry.

Our project also owes a great deal to the Ruby on Rails community. What little we achieved was possible because we have built on the libraries of giants.


\prefaceTOC   % Table of Contents
\prefaceLOF   % List of Figures
\prefaceLOT   % List of Tables


\chapter*{List of Abbreviations}

\begin{tabular}[t]{l@{\hspace*{2cm}}l}
  BPMN & Business Process Model and Notation \\
  DSL & Domain-specific language \\
  JVM & Java Virtual Machine \\
  MVC & Model-view-controller \\
  MTI & Multiple Table Inheritance \\
  ORM & Object-Relational Mapper \\
\end{tabular}

\endpreface

\end{document}
